Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterparts
of $\va,\vp,\vn$ with maximum embedding move distance off their original
locations, \ie,
$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
$\tilde{\va}=\phi(X+r^*)$, and $r^*=\arg\max_{r}d_\phi(X+r, X)$.
%
The $\tilde{\vp}$ and $\tilde{\vn}$ are obtained similarly.

@@

Anti-Collapse Triplet (ACT)~\cite{robrank} ``collapses'' the embedding vectors
of positive and negative sample, and enforces the model to separate them apart,
\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
d_\phi(X_p+r_p, X_n+r_n)$.

@@

>>>>

Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterparts
of $\va,\vp,\vn$ with maximum embedding move distance off their original
locations, \ie,
%
\begin{equation}
%
L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)
%
\end{equation}
%
where
$\tilde{\va}=\phi(\mA+\vr^*)$, and $\vr^*=\arg\max_{\vr}d_\phi(\mA+\vr, \mA)$.
%
The $\tilde{\vp}$ and $\tilde{\vn}$ are obtained similarly.

@@

Anti-Collapse Triplet (ACT)~\cite{robrank} ``collapses'' the embedding vectors
of positive and negative sample, and enforces the model to separate them apart,
\ie,
%
\begin{align}
%
	L_\text{ACT} &=L_\text{T}(\va, \overrightarrow{\vp},
\overleftarrow{\vn};\gamma),\\
%
	[\overrightarrow{\vp},\overleftarrow{\vn}] & =[\phi(\mP+\vr_p^*), \phi(\mN+\vr_n^*)]\\
%
	[\vr_p^*,\vr_n^*] &= \argmin_{\vr_p,\vr_n} d_\phi(\mP+\vr_p, \mN+\vr_n).
%
\end{align}

@@

\noindent\textbf{I. Range of Hardness.}

As reflected in Sec.~3.1 and Fig.~2, the range of $H(\cdot)$ is $[-2, 2]$.
%
The embedding vectors have been normalized to the real unit hypersphere
as pointed out in the manuscript.
%
And the range of distance between any two points on the hypersphere is
$[0,2]$.
%
Hence
%
\begin{align}
	& \max H(\mA, \mP, \mN)\\
	=& \max [d_\phi(\mA, \mP) - d_\phi(\mA, \mN)]\\
	=& \max [d_\phi(\mA, \mP)] - \min [d_\phi(\mA, \mN)]\\
	=& 2 - 0,
\end{align}
%
\begin{align}
	& \min H(\mA, \mP, \mN)\\
	=& \min [d_\phi(\mA, \mP) - d_\phi(\mA, \mN)]\\
	=& \min [d_\phi(\mA, \mP)] - \max [d_\phi(\mA, \mN)]\\
	=& 0 - 2.
\end{align}
%
Namely $H(\cdot)\in[-2,2]$. Meanwhile, since
%
\begin{equation}
%
L_\text{T}(\mA, \mP, \mN; \gamma) = \max(0, H(\mA, \mP, \mN) + \gamma),
%
\end{equation}
%
we have $L_\text{T}\in[0, 2+\gamma]$.
